\documentclass[12pt]{article}
\usepackage{amsfonts}
\usepackage{amsbsy}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{rotating}
\usepackage{graphics}
\usepackage{epstopdf}
\usepackage{pdfsync}
\usepackage{natbib}
\usepackage{caption}
\usepackage{xcolor}
\usepackage{hyperref}

\textheight 9.2 in \textwidth 6.4 in
\topmargin -0.15 in       % for PC
\topmargin -0.7 in       % for Unix
\oddsidemargin 0.10in %\evensidemargin 0.0in
\parskip=.00in
\renewcommand{\baselinestretch} {1.2}
\makeatletter \setcounter{page}{1}
\def\singlespace{\def\baselinestretch{1}\@normalsize}
\def\endsinglespace{}

\@addtoreset{equation}{section}
\renewcommand{\theequation} {\arabic{section}.\arabic{equation}}
\renewcommand{\thefigure}{\arabic{figure}}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
\newcommand{\distas}[1]{\mathbin{\overset{#1}{\kern\z@\sim}}}%


% begin definition
\def\conas{\stackrel{a.s.} {\rightarrow}}         % conv. a.s.
\def\conP{\stackrel{\cal P} {\rightarrow}}        % conv. in probability
\def\conD{\stackrel{\cal D} {\rightsquigarrow}}        % conv. in distribution
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\argmax}{argmax}
\def\iid{\stackrel{ iid} {\sim}}          % i.i.d
\def\hat{\widehat}
\def\tilde{\widetilde}

%general sets
\def\cal{\mathcal}
\def\calA{{\cal A}} %Action sets
\def\calB{{\cal B}} %Bounded set
\def\calC{{\cal C}} %Convex set
\def\calH{{\cal H}} %Hilbert Space
\def\calS{{\cal S}} %A regular set
\def\calNr{{\cal N}_r} %Neighborhood
\def\calX{{\cal X}} %Covariate space
\def\calF{{\cal F}} %Function space

%special sets
\def\bbR{{\mathbb{R}}} %Real number
\def\bbN{{\mathbb{N}}}%Natural number
\def\bbQ{{\mathbb{Q}}} %Rational number
\def\bbZ{{\mathbb{Z}}} %Integer

%Matrix
\def\bA{{\bf A}}
\def\bB{{\bf B}}
\def\bC{{\bf C}}
\def\bD{{\bf D}}
\def\bH{{\bf H}}
\def\bI{{\bf I}}
\def\bJ{{\bf J}}
\def\bP{{\bf P}}
\def\bT{{\bf T}}
\def\bW{{\bf W}}
\def\bX{{\bf X}}

%vector
\def\balpha{{\boldsymbol \alpha}}
\def\bbeta{{\boldsymbol \beta}}
\def\btheta{{\boldsymbol \theta}}

\def\bzero{{\bf 0}}
\def\bone{{\bf 1}}
\def\bbf{{\bf f}}
\def\br{{\bf r}}
\def\by{{\bf y}}

%notations
\def\sign{{\mathrm{sign}}}
\def\var{{\mathrm{var}}}
\def\cov{{\mathrm{cov}}}
\def\ind{\perp\!\!\!\perp}

%others
\def\mif{\mathrm{if}\ }
\def\ow{\mathrm{otherwise}\ }
\def\st{\mathrm{subject\ to}\quad }
\def\diag{\mathrm{diag}}
\def\minimize{\mathrm{minimize}\quad }
\def\maximize{\mathrm{maximize}\quad }
\def\dom{{\rm dom}}



\begin{document}
\title
{\bf My Data Science Challenging Problems \# 53: Streaming Data Analytics for M- and Z- estimators}
\author
{
Drafted by Haoda Fu\\
XXX \\
XXXX \\
\textsl{xxx} }
\date{\today}

\maketitle
\begin{abstract}
\textbf{{\color[rgb]{1,0,0} If you happen to have a solution of this question, please contact Haoda Fu at \href{mailto:fu\_haoda@lilly.com }{fu\_haoda@lilly.com} or  \href{mailto:ffuhaoda@gmail.com}{fuhaoda@gmail.com}  or commit your solution to \url{git@github.com:fuhaoda/DCSP53_StreamingDataAnalytics.git} }
}

\end{abstract}

\noindent {\bf Key words and Phrases}: *** ***.

\noindent {\bf Short title}: ***
\section{Introduction}
As an example, if we are interested in to calculate the mean value of $X_1,\cdots, X_{100}$.
The traditional approach is to save all the 100 numbers then take the average. For streaming data analytics, we only need to save the $\bar{X}_n$ and $n$, then when the $X_{n+1}$ comes in, we can update the results as $\bar{X}_{n+1} = \frac{n \bar{X}_n + X_{n+1}}{n+1}$.

Streaming data analytic is an important area for digital health. Many of the analytic problems are end up as M- or Z- estimators. How can we build up streaming data analytics for M- and Z- estimators?

\section{Definition}
Suppose that we are interested in a parameter (or functional) $\theta$ attached to the distribution of observations $X_1,\cdots, X_n$. A popular method for finding an estimator $\hat{\theta}_n = \hat{\theta}_n(X_1,\cdots, X_n)$ is to maximize a criterion function of the type,
\begin{align*}
\theta & \mapsto M_n(\theta) = \frac{1}{n} \sum_{i=1}^n m_{\theta} (X_i).
\end{align*} 
Here $m_{\theta} : \calX \mapsto \bbR$ are known functions. An estimator maximizing $M_n(\theta)$ over $\Theta$ is called an \emph{M-estimator}. 

As related, some of problems are defined to find solution of,
\begin{align*}
Z_n(\theta) &= \frac{1}{n} \sum_{i=1}^n Z_{\theta}(X_i)=0,
\end{align*}
where $Z_{\theta}$ are known vector-valued maps.  Such estimator is called \emph{Z-estimator} (for zero). 

Suppose the data $X_1, X_2, X_3, \cdots$ are coming in sequence. How can we continue to update our estimator of $\theta$.  So a few related questions,
\begin{enumerate}
	\item We cannot save all the $X_i$, what information do we need to save so that we can have asymptotic distribution of $\theta$ correctly.
	\item What are the efficient updating algorithms for the mean and variance estimation?
	\item How can we design \texttt{C++} codes so that it can be broadly used.
\end{enumerate}

The solution could be related stochastic gradient decent approach. We also need some efficient solution, such as modified limited memory BFGS algorithms. 


\section{Framework}



\section*{Appendix: Proof of Equation ()}.




\bibliographystyle{/Users/c082213/BoxSync/Help/References/asa_HD}
\bibliography{/Users/c082213/BoxSync/Help/References/MyStats}


\end{document}
